Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-02-08 manuscript/cpcrw_manuscript.Rmd
Added two figures (fluxes over time)

---
title: "Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils"
author: "Ben Bond-Lamberty, Peyton Smith, Vanessa Bailey"
#date: "February 1, 2016"
output: html_document
---

@@

```{r, echo=FALSE}
# compute outlier and exclusion numbers
sdn <- readLines("../outputs/summarydata.csv") %>% length
sdcn <- readLines("../outputs/summarydata_clean.csv") %>% length
en <- readLines("../outputs/3-remove/excluded_data.csv") %>% length
rn <- readLines("../outputs/3-remove/removed_data.csv") %>% length
```

@@

```{r kable, echo=FALSE}
# Print out the `WC_effect` data frame in a nice-looking table
WC_effect$Gas[WC_effect$Gas == "CO2"] <- "CO<sub>2</sub>"  # html
WC_effect$Gas[WC_effect$Gas == "CH4"] <- "CH<sub>4</sub>"  # html
knitr::kable(WC_effect, digits = 3, 
             col.names = c("Treatment", "Temperature", "Gas", "R<sup>2</sup>", "Sigma", "P", "AIC"))
```

@@

**Figure 2.** A faceted (Temperature ~ Treatment) plot showing normalized flux means and errors by incubation time. (Basically the figure already in the README diagnostics.)

**Figure 3.** Cumulative fluxes over the incubation.

>>>>

---
title: Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils
author: "Ben Bond-Lamberty, Peyton Smith, Vanessa Bailey"
output: html_document
---

@@

```{r, echo=FALSE}
# TODO: this isn't good--fragile if files move or change names
# Want everything in-memory (or something)
# Compute outlier and exclusion numbers
sdn <- readLines("../outputs/summarydata.csv") %>% length
sdcn <- readLines("../outputs/summarydata_clean.csv") %>% length
en <- readLines("../outputs/3-remove/excluded_data.csv") %>% length
rn <- readLines("../outputs/3-remove/removed_data.csv") %>% length
```

@@

```{r kable, echo=FALSE}
# Print out the `WC_effect` data frame in a nice-looking table
WC_effect$Gas[WC_effect$Gas == "CO2"] <- "CO<sub>2</sub>"  # html
WC_effect$Gas[WC_effect$Gas == "CH4"] <- "CH<sub>4</sub>"  # html
knitr::kable(WC_effect, digits = 3, col.names = c("Gas", "Treatment", "Temperature", "R<sup>2</sup>", "Sigma", "P", "AIC"))
```

@@

**Figure 2.** A faceted (Temperature ~ Treatment) plot showing normalized CO2 flux means and errors by incubation time. (Basically the figure already in the README diagnostics.)

```{r, echo=FALSE}
print(figureB)
```

**Figure 3.** A faceted (Temperature ~ Treatment) plot showing normalized CH4 flux means and errors by incubation time. (Basically the figure already in the README diagnostics.)

```{r, echo=FALSE}
print(figureC)
```

**Figure 4.** Cumulative fluxes over the incubation.
